Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2

### 2023-05-17 paper.tex
Add long arg recomb intervals figure

\subsection{Distribution of recombination breakpoint intervals}
\label{sec:breakpoint_intervals}
It is rarely possible to be precise about the position on the genome at which
a recombinant sequence switches from inheriting from one parent to another.
Even if we observe the recombinant sequence before signficant
divergence occurs (during onward transmission), if the two parent sequences
are similar there is no way to distinguish them. Here we define the
interval for a particular breakpoint as the genome coordinates over which the
sequences for the left and right parent nodes are identical. The right-hand
extreme of the breakpoint interval is chosen by the LS HMM Viterbi algorithm
(Section~\ref{sec:ls}) and the left bound can then be derived by
sequence comparison of the parents.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/recombination_intervals.pdf}
\caption{\label{fig:breakpoint-distribution}
Distribution of recombination breakpoints and mutations along the genome.}
\end{figure}

@@

>>>>

\subsection{Distribution of recombination breakpoint intervals}
\label{sec:breakpoint_intervals}
It is rarely possible to be precise about the position on the genome at which
a recombinant sequence switches from inheriting from one parent to another.
Even if we observe the recombinant sequence before signficant
divergence occurs (during onward transmission), if the two parent sequences
are similar there is no way to distinguish them. Here we define the
interval for a particular breakpoint as the genome coordinates over which the
sequences for the left and right parent nodes are identical. The right-hand
extreme of the breakpoint interval is chosen by the LS HMM Viterbi algorithm
(Section~\ref{sec:ls}) and the left bound is then derived by
sequence comparison of the parents.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/wide_arg_recombination_intervals.pdf}
\caption{\label{fig:breakpoint-distribution}
Distribution of recombination breakpoints and mutations along the genome in
the Wide ARG.
See Figure~\ref{fig:long_arg_breakpoint_distribution} for the equivalent plot
for the Long ARG.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/long_arg_recombination_intervals.pdf}
\caption{\label{fig:long_arg_breakpoint_distribution}
Distribution of recombination breakpoints and mutations along the genome in
the Long ARG.}
\end{figure}
